### 2018-02-08 master/paper.tex
Final ver.

In embedded network software running on embedded systems within the Internet of Things (IoT), high levels of runtime efficiency and user productivity are required.
To improve productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
Based on the above information, this thesis proposes an extended mruby on TECS framework for its application in developing software for IoT devices, including sensors and actuators.
The proposed framework enables mruby programs to utilize Tomakomai Internetworking (TINET), a TCP/IP protocol stack specifically designed for use in embedded systems.
Further, this thesis proposes two component-based functionalities, i.e., a componentized TINET stack called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
Here, TINET+TECS improves scalability and configurability and offers software developers high levels of productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
Futher, TLSF+TECS is a thread-safe memory allocator that runs at high speeds and efficiently consumes memory.
The experimental results of the comparison between TINET+TECS and the original TINET show that execution time and memory consumption overhead are both reduced; I conclude that configurability is improved.
Finally, the TLSF+TECS functionality which obtains and report statistical information regarding mruby's virtual machine (VM) memory usage and frequency of memory requests, helps developers debug and verify their embedded IoT systems.

@@

In addition to specific development environments, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to develop quality software.
Currently, most embedded software is implemented using the C language.
However, development in C typically results in large code size, high costs, and significant development time.
In contrast, the use of scripting languages improves efficiency of software engineering and can shorten the development period because it effectively supports and promotes the development of reusable scripts.

@@

In this thesis, TOPPERS/ASP3 \cite{par:ASP3},\cite{url:ASP3} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2},\cite{par:hr-tecs}.

@@

{\bf Application layer:}
An application in TINET+TECS is implemented as a component such as tApplication.
Software with TINET uses ITRON TCP/IP API \cite{url:ITRON_TCP/IP_API_Spec} such as {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat}.
In TINET+TECS, the application component calls TECS functions such as {\it cTCPAPI\_sendData} and {\it cTCPAPI\_receiveData}.
Moreover, in TINET+TECS supporting a TECS adapter, an existing application with TINET can run on the TINET+TECS framework without transporting, and therefore, software can be developed either using existing methods or as TECS components.

@@

{\bf Network layer:}
The tIPv4Input and tIPv4Output components perform, respectively, the receiving and sending processing in the network layer.
The tIPv4Functions component performs functions such as checksum, the tICMP component is used for the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.

@@

{\bf Physical layer:}
The tNetworkInterfaceContoroller component implements a network device driver.
Software can be run on other devices by replacing the component because only the component depends on the target device.

@@

A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11--13 in Fig. \ref{src:DynamicCDLcode}).
The cREP port is defined using {\it [dynamic]} to identify the call port used to dynamically switch the components.
The call port with the {\it [dynamic]} specifier is not optimized and is allocated in RAM using a plug-in.

@@

{\bf Efficient memory consumption.}
Memory efficiency is improved by suppressing memory fragmentation.
Various experiments have achieved an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.

@@

The proposed framework uses the TLSF memory allocator for memory management within RiteVMs; however, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple threads, memory contention will likely occur.
Here, as a RiteVM allocates and deallocates memory at high frequencies, memory contention quickly occurs when multiple RiteVMs are instantiated.

@@

In the proposed framework, applications can call TINET functions, such as specific TCP- and UDP-related functions, from mruby programs because the mruby-TECS bridge automatically generates the code to link mruby and C.
Fig. \ref{src:mruby} shows an example mruby program that transmits the value acquired from a sensor from the senser to another device.
In general, mruby makes it easier to develop applications than using C with the existing TINET framework.

@@

The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
For {\it tcp\_snd\_dat}, I measured the executing time starting from the API call through the application until the return of the processing result.
In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig. \ref{fig:ComponentProtocolStack}.
For {\it tcp\_rcv\_dat}, I measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 us.
As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \caption{Component diagrams for without/with dynamic connection}
    \label{fig:ComparisonOfDynamicConnection}
\end{figure}

Memory consumption without and with TECS dynamic connection was then evaluated.
As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right of Fig. \ref{fig:ComparisonOfDynamicConnection}.
Even if the number of REPs increases, additional call ports can be joined through the selector, instead of the CEPs.

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \caption{Memory consumption in two cases (with/without dynamic connection)}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

\begin{table}[t]
    \centering
    \caption{CDL code lines of without/with dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \begin{minipage}[t]{0.5\hsize}
  \centering
  \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    cREP[1] = REP_001.eREP;
    ...
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    cREP[1] = REP_001.eREP;
    ...
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    cREP[1] = REP_001.eREP;
    ...
    cREP[n] = REP_00n.eREP;
};
  \end{lstlisting}
 \end{minipage}
 \begin{minipage}[t]{0.5\hsize}
  \centering
  \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    cREP[1] = REP_001.eREP;
    ...
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
...
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
  \end{lstlisting}
 \end{minipage}
 \caption{Two CDL codes (without/with dynamic connection)}
 \label{src:ComparisonOfCDL}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/EvaluationOfAdapter.pdf}
    \caption{Execution times in two cases (without/with TECS adapter)}
    \label{fig:EvaluationOfAdapter}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=11cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
    \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
    \label{fig:EvaluationOfTLSFStatistics}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=11cm,clip]{figure/EvaluationOfTLSFFrequency.pdf}
    \caption{Memory frequency of RiteVM (mruby VM) by TLSFStatistics component}
    \label{fig:EvaluationOfTLSFFrequency}
\end{figure}

@@

\begin{table*}[t]
    \caption{Comparison of open-source TCP/IP protocol stacks for embedded systems}
    \label{tab:TCP/IP}
    \centering
    {\small \tabcolsep = 1mm
    \begin{tabular}{c||ccccccc}
        \hline\hline
        & \shortstack{Configurability}
        & \shortstack{Generation} 
        & \shortstack{Binding} 
        & \shortstack{Support CBD} 
        & \shortstack{Memory saving} \\ \hline
        uIP \cite{par:uIP}     & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
        lwIP \cite{par:lwIP}   & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
        TINET \cite{url:TINET} &            & Static     & Dynamic  &              & \checkmark \\
        Proposed framework     & \checkmark & Static     & Dynamic  & \checkmark   & \checkmark \\
    \end{tabular}
    }
\end{table*}

@@

\begin{acknowledgment}
I would like to express my deep sense of gratitude to my adviser Professor Toshimitsu Ushio and Assistant Professor Takuya Azumi, Graduate School of Engineering Science, Osaka University, for their invaluable, constructive advice and constant encouragement during this work.
Professor Ushio and Assistant Professor Azumi's deep knowledge and their eyes for detail have inspired me much.
I am deeply grateful to my advisers Hiroshi Oyama and Hiroaki Nagashima for their helpful comments on this thesis and warm encouragement.
Finally, I would like to thank all members of Ushio Laboratory, especially the members of the Azumi team, for their kind help and cooperation.
\end{acknowledgment}

@@

\section*{Domestic Conference}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
    ``Componentized Dynamic Memory Allocator for Embedded Systems,''
    \emph{in Proceedings of IPSJ Kansai-Branch Convention 2017},
    A-3, 2017 (in Japanese).
\item
    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
    ``mruby Bytecode Loader Using Bluetooth in Multi-VM Environment,''
    \emph{in Proceedings of ETNET2016},
    No.8, pp.1-6, 2016 (in Japanese).
\end{enumerate}

>>>>

In embedded network software running on embedded systems within the Internet of Things (IoT), high levels of runtime efficiency and user productivity are required.
To improve productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
Based on the above information, this thesis proposes an extended mruby on TECS framework for its application in developing software for IoT devices, including sensors and actuators.
The proposed framework enables mruby programs to utilize Tomakomai Internetworking (TINET), a TCP/IP protocol stack specifically designed for use in embedded systems.
Further, this thesis proposes two component-based functionalities, i.e., a componentized TINET stack called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
Here, TINET+TECS improves scalability and configurability and offers software developers high levels of productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
Further, TLSF+TECS is a thread-safe memory allocator that runs at high speeds and efficiently consumes memory.
The experimental results of the comparison between TINET+TECS and the original TINET show that execution time and memory consumption overhead are both reduced; I conclude that configurability is improved.
Finally, the TLSF+TECS functionality which obtains and report statistical information regarding mruby's virtual machine (VM) memory usage and frequency of memory requests, helps developers debug and verify their embedded IoT systems.

@@

In addition to specific development environments, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to develop quality software.
Currently, most embedded software is implemented using the C language.
However, development in C typically results in large code size, high costs, and significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it effectively supports and promotes the development of reusable scripts.

@@

In this thesis, TOPPERS/ASP3 \cite{par:ASP3},\cite{url:ASP3} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON}.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2},\cite{par:hr-tecs}.

@@

{\bf Application layer:}
An application in TINET+TECS is implemented as a component such as tApplication.
Software with TINET uses ITRON TCP/IP API \cite{url:ITRON_TCP/IP_API_Spec} such as {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat}.
In TINET+TECS, the application component calls TECS functions such as {\it cTCPAPI\_sendData} and {\it cTCPAPI\_receiveData}.
Moreover, in TINET+TECS supporting a TECS adapter, an existing application with TINET can run on the TINET+TECS framework without transporting, and therefore, the software can be developed either using existing methods or as TECS components.

@@

{\bf Network layer:}
The tIPv4Input and tIPv4Output components perform, respectively, the receiving and sending processing in the network layer.
The tIPv4Functions component performs functions such as a checksum, the tICMP component is used for the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.

@@

{\bf Physical layer:}
The tNetworkInterfaceContoroller component implements a network device driver.
The software can be run on other devices by replacing the component because only the component depends on the target device.

@@

A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11-13 in Fig. \ref{src:DynamicCDLcode}).
The cREP port is defined using {\it [dynamic]} to identify the call port used to dynamically switch the components.
The call port with the {\it [dynamic]} specifier is not optimized and is allocated in RAM using a plug-in.

@@

{\bf Efficient memory consumption.}
Memory efficiency is improved by suppressing memory fragmentation.
Various experiments have achieved an average fragmentation of less than 15 \% and a maximum fragmentation of less than 25 \%.

@@

The proposed framework uses the TLSF memory allocator for memory management within RiteVMs; however, since it is difficul to handle multiple memory pools in the existing TLSF, if memory is allocated or deallocated from multiple threads, memory contention will likely occur.
Here, as a RiteVM allocates and deallocates memory at high frequencies, memory contention quickly occurs when multiple RiteVMs are instantiated.

@@

In the proposed framework, applications can call TINET functions, such as specific TCP- and UDP-related functions, from mruby programs because the mruby-TECS bridge automatically generates the code to link mruby and C.
Fig. \ref{src:mruby} shows an example mruby program that transmits the value acquired from a sensor from the sensor to another device.
In general, mruby makes it easier to develop applications than using C with the existing TINET framework.

@@

The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
For {\it tcp\_snd\_dat}, I measured the executing time starting from the API call through the application until the return of the processing result.
In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig. \ref{fig:ComponentProtocolStack}.
For {\it tcp\_rcv\_dat}, I measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
The execution time of TINET+TECS is close to that of TINET, with an overhead of about three us.
As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \caption{Component diagrams for without/with the dynamic connection}
    \label{fig:ComparisonOfDynamicConnection}
\end{figure}

Memory consumption without and with TECS the dynamic connection was then evaluated.
As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right of Fig. \ref{fig:ComparisonOfDynamicConnection}.
Even if the number of REPs increases, additional call ports can be joined through the selector, instead of the CEPs.

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \caption{Memory consumption in two cases (with/without the dynamic connection)}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

\begin{table}[t]
    \centering
    \caption{CDL code lines of without/with the dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \begin{minipage}[t]{0.5\hsize}
  \centering
  \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    cREP[1] = REP_001.eREP;
    ...
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    cREP[1] = REP_001.eREP;
    ...
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    cREP[1] = REP_001.eREP;
    ...
    cREP[n] = REP_00n.eREP;
};
  \end{lstlisting}
 \end{minipage}
 \begin{minipage}[t]{0.5\hsize}
  \centering
  \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    cREP[1] = REP_001.eREP;
    ...
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
...
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
  \end{lstlisting}
 \end{minipage}
 \caption{Two CDL codes (without/with the dynamic connection)}
 \label{src:ComparisonOfCDL}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/EvaluationOfAdapter.pdf}
    \caption{Execution times in two cases (without/with the TECS adapter)}
    \label{fig:EvaluationOfAdapter}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
    \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
    \label{fig:EvaluationOfTLSFStatistics}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/EvaluationOfTLSFFrequency.pdf}
    \caption{Memory frequency of RiteVM (mruby VM) by TLSFStatistics component}
    \label{fig:EvaluationOfTLSFFrequency}
\end{figure}

@@

\begin{table*}[t]
    \caption{Comparison of open-source TCP/IP protocol stacks for embedded systems}
    \label{tab:TCP/IP}
    \centering
    {\small \tabcolsep = 1mm
    \begin{tabular}{c||ccccccc}
        \hline\hline
        & \shortstack{Configurability}
        & \shortstack{Generation} 
        & \shortstack{Binding} 
        & \shortstack{Support CBD} 
        & \shortstack{Memory saving} \\ \hline
        uIP \cite{par:uIP}     &  Partially & Dynamic    & Dynamic  &              & \checkmark \\
        lwIP \cite{par:lwIP}   &  Partially & Dynamic    & Dynamic  &              & \checkmark \\
        TINET \cite{url:TINET} &            & Static     & Dynamic  &              & \checkmark \\
        Proposed framework     & \checkmark & Static     & Dynamic  & \checkmark   & \checkmark \\
    \end{tabular}
    }
\end{table*}

@@

\begin{acknowledgment}
I would like to express my deep sense of gratitude to my adviser Assistant Professor Takuya Azumi, Professor Toshimitsu Ushio, and Associate Professor Takafumi Kanazawa,  Graduate School of Engineering Science, Osaka University, for their invaluable, constructive advice and constant encouragement during this work.
Assistant Professor Azumi's deep knowledge and their eyes for detail have inspired me much.
I am deeply grateful to my advisers Hiroshi Oyama and Hiroaki Nagashima for their helpful comments on this thesis and warm encouragement.
I would like to thank all members of Ushio Laboratory, especially the members of the Azumi team, for their kind help and cooperation.
Finally, I would also like to express my gratitude to my family for their moral support and warm encouragements.
\end{acknowledgment}

@@

\section*{Domestic Conference}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
    ``Componentized Dynamic Memory Allocator for Embedded Systems,''
    \emph{In Proceedings of IPSJ Kansai-Branch Convention 2017},
    A-3, 2017 (in Japanese).
\item
    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
    ``mruby Bytecode Loader Using Bluetooth in Multi-VM Environment,''
    \emph{In Proceedings of ETNET2016},
    No.8, pp.1-6, 2016 (in Japanese).
\end{enumerate}
